upwell_IDX

### 2019-08-18 upwell_IDX.Rmd
updating

```{r}
# Loading the insitu temperature data along the wc
load("Data/SACTN_US.RData")
# exceedance <-
#   function(data,
#            x = t,
#            y = temp,
#            threshold,
#            below = FALSE,
#            minDuration = 5,
#            joinAcrossGaps = TRUE,
#            maxGap = 2,
#            maxPadLength = 3)
# Upwelling temperature threshold 12.4 / 30th percentile
SACTN_upwell <- UI_angle %>% 
  dplyr::rename(temp = ui.saws) %>%
  group_by(site) %>%
  # mutate(min_t = min(t), 
  #        max_t = max(t)) %>% 
  nest() %>% 
  mutate(clim = purrr::map(data, ts2clm, climatologyPeriod = c("2000-01-01", "2005-12-31")),
         # NB: A threshold of 3 appeared to be far to strict
         exceed = purrr::map(clim, exceedance, minDuration = 1, threshold = 1)) %>% 
  # mutate() %>% 
  select(-data, -clim) %>% 
  unnest() %>%
  filter(row_number() %% 2 == 1) %>%
  unnest() %>% 
  dplyr::rename(ui.saws = temp) %>% 
  select(site, t, ui.saws, exceedance)

@@

# Unpack the event metric reults
SACTN_upwell_events <- SACTN_upwell_base %>% 
  unnest() %>%
  filter(row_number() %% 2 == 0) %>%
  unnest()
# Unpack the daily climatology results
SACTN_upwell_clims <- SACTN_upwell_base %>% 
  unnest() %>%
  filter(row_number() %% 2 == 1) %>% 
  unnest()

# The above chunk of code appears to work as expected.
# What needs to be done now is that the thresholds for duration and UI strength need to be justified/decided uopn.
# What also needs to be decided is if we are interested in any upwelling results throughout the year,
# or only during the upwelling season, whenever that may be for each site.
# I think we have demonstrated the technical capability needed to answer the question of whether or not upwelling
# is changing over time.
# Now we really need to focus on which of these parameters need to best be tweaked to answer that question.

# Linear Models
lm_coeff <- function(df){
  res <- lm(formula = val ~ date_peak, data = df)
  res_coeff <- round(as.numeric(res$coefficient[2]), 4)
}

# Changes in upwelling metrics
SACTN_upwell_lm <- SACTN_upwell_events %>% 
  select(-c(index_start:index_end)) %>% 
  gather(key = "var", value = "val", -c(site:date_end)) %>% 
  group_by(site, var) %>% 
  nest() %>% 
  mutate(slope = purrr::map(data, lm_coeff)) %>% 
  select(-data) %>% 
  unnest() %>% 
  # convert from daily to decadal values
  mutate(slope = slope * 365.25*10)

```

@@

```

@@

# UI_angle_season <- UI_angle %>%
#   mutate(month = month(t, abbr = T, label = T)) %>%
#   mutate(season = ifelse(month %in% c("Jan", "Feb", "Mar"), "Summer",        
#                           ifelse(month %in% c("Apr", "May", "Jun"), "Autumn",
#                               ifelse(month %in% c("Jul", "Aug", "Sep"), "Winter",
#                                       ifelse(month %in% c("Oct", "Nov", "Dec"), "Spring","Error")))))

## save(UI_angle_season, file = "Data/UI_angle_season.RData")

load("Data/UI_angle_season.RData")
```

# Show how winds intensified over the years
# Show how upwwelling intensified over the years
# Look at upwelling seasonally

>>>>

```{r}
# Loading the insitu temperature data along the wc
load("Data/SACTN_US.RData")
# exceedance <-
#   function(data,
#            x = t,
#            y = temp,
#            threshold,
#            below = FALSE,
#            minDuration = 5,
#            joinAcrossGaps = TRUE,
#            maxGap = 2,
#            maxPadLength = 3)
# Upwelling temperature threshold 12.4 / 30th percentile
SACTN_upwell <- UI_angle %>% 
  dplyr::rename(temp = ui.saws) %>%
  group_by(site) %>%
  # mutate(min_t = min(t), 
  #        max_t = max(t)) %>% 
  nest() %>% 
  mutate(clim = purrr::map(data, ts2clm, climatologyPeriod = c("2000-01-01", "2005-12-31")),
         # NB: A threshold of 3 appeared to be far to strict
         exceed = purrr::map(clim, exceedance, minDuration = 1, threshold = 1)) %>%  #Upwelling cannot be descrbed as an event. Upwelling can last for a few hours. Given that we have daily data, upwelling events minimum duration here will be 1day
  # mutate() %>% 
  select(-data, -clim) %>% 
  unnest() %>%
  filter(row_number() %% 2 == 1) %>%
  unnest() %>% 
  dplyr::rename(ui.saws = temp) %>% 
  select(site, t, ui.saws, exceedance)

@@

# Unpack the event metric reults
SACTN_upwell_events <- SACTN_upwell_base %>% 
  unnest() %>%
  filter(row_number() %% 2 == 0) %>%
  unnest()
# save(SACTN_upwell_events, file = "Data/SACTN_upwell_events.RData")

# Unpack the daily climatology results
SACTN_upwell_clims <- SACTN_upwell_base %>% 
  unnest() %>%
  filter(row_number() %% 2 == 1) %>% 
  unnest()
# save(SACTN_upwell_clims, file = "Data/SACTN_upwell_clims.RData")

# The above chunk of code appears to work as expected.
# What needs to be done now is that the thresholds for duration and UI strength need to be justified/decided uopn. 
    # Min duration for an upwelling event - 1day and threshold -1
# What also needs to be decided is if we are interested in any upwelling results throughout the year,
# or only during the upwelling season, whenever that may be for each site.
# I think we have demonstrated the technical capability needed to answer the question of whether or not upwelling
# is changing over time.
# Now we really need to focus on which of these parameters need to best be tweaked to answer that question.
```

@@

# Linear Models
lm_coeff <- function(df){
  res <- lm(formula = val ~ date_peak, data = df)
  res_coeff <- round(as.numeric(res$coefficient[2]), 4)
}
# Changes in upwelling metrics
SACTN_upwell_lm <- SACTN_upwell_events %>% 
  select(-c(index_start:index_end)) %>% 
  gather(key = "var", value = "val", -c(site:date_end)) %>% 
  group_by(site, var) %>% 
  nest() %>% 
  mutate(slope = purrr::map(data, lm_coeff)) %>% 
  select(-data) %>% 
  unnest() %>% 
  # convert from daily to decadal values
  mutate(slope = slope * 365.25*10)
```

@@

season_func <- function(df){
  season <- df %>%
  mutate(month = month(t, abbr = T, label = T),
         year = year(t)) %>%
  mutate(season = ifelse(month %in% c("Jan", "Feb", "Mar"), "Summer",
                          ifelse(month %in% c("Apr", "May", "Jun"), "Autumn",
                              ifelse(month %in% c("Jul", "Aug", "Sep"), "Winter",
                                      ifelse(month %in% c("Oct", "Nov", "Dec"), "Spring","Error")))))
return(season)
}

# UI_angle_season <- season_func(df = UI_angle)
# save(UI_angle_season, file = "UI_angle_season.RData")

load("Data/UI_angle_season.RData")

# Speed of wind increased over time???
anova_func <- function(df){
  season_aov <- aov(mean_speed ~ site  * year * season, data = df)
return(season_aov)
}

wind_speed_aov <- anova_func(df = UI_angle_season)
summary(wind_speed_aov)

anova_func <- function(df){
  season_aov <- aov(ui.saws ~ site  * year * season, data = df)
return(season_aov)
}
ui.saws_aov <- anova_func(df = UI_angle_season)
summary(ui.saws_aov)
```
